A seamless, client-centric programming model for type safe web applications

### 2014-05-08 paper.tex
ServerDummy + RemoteDummy

\begin{code}
data Server a = Server
data Remote a = Remote CallID [JSON]
\end{code}

@@

\begin{code}
liftServerIO :: IO a -> App (Server a)
liftServerIO _ = App Server
\end{code}

@@

\begin{code}
newtype Server a = Server (ReaderT SessionInfo IO a)
  deriving (Functor, Applicative, Monad, MonadIO)
data Remote a = Remote
\end{code}

@@

\begin{code}
remote f = App $ do
  (next_id, remotes) <- get
  put (next_id+1, (next_id, mkRemote f) : remotes)
  return Remote
\end{code}

>>>>

\begin{code}
data Server a = ServerDummy
data Remote a = Remote CallID [JSON]
\end{code}

@@

\begin{code}
liftServerIO :: IO a -> App (Server a)
liftServerIO _ = App ServerDummy
\end{code}

@@

\begin{code}
newtype Server a = Server (ReaderT SessionInfo IO a)
  deriving (Functor, Applicative, Monad, MonadIO)
data Remote a = RemoteDummy
\end{code}

@@

\begin{code}
remote f = App $ do
  (next_id, remotes) <- get
  put (next_id+1, (next_id, mkRemote f) : remotes)
  return RemoteDummy
\end{code}
